TacticToe: Learning the Game of Tactics

### 2018-02-07 tactictoe_jv.tex
some minor modifications in section 2 + example of prettified script

\begin{definition}(search tree)\\
A search tree $\mathfrak{T}$ is a sixtuple
$(\mathbb{T},\mathbb{G},\mathbb{A},T,G,A)$
that respects the following conditions:
\begin{itemize}
\item $\mathbb{T}$ is a set of tactics, $\mathbb{G}$ is a set of goals
 and $\mathbb{A}$ is a set of nodes. These sets contains only objects
 appearing in the search tree.
\item $T$ is a total function from $\mathbb{G}$ to $\mathcal{P}(\mathbb{T})$. It takes a
goal and return the set of tactics already applied to this goal.
\item $G$ is a total function from $\mathbb{A}$ to $\mathcal{P}(\mathbb{G})$. It takes a
node and returns the set of goals in this node.

\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. It takes a goal and a tactic and returns the node produced by the
application of the tactic to the goal, if this tactic has been applied to this
goal. Its support $\mathit{Support}(A)$ is by definition $\lbrace (g,t)\ |\ t \in T(g)
\rbrace$.
\item If $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$.
\end{itemize}

@@

\begin{figure}{}
\begin{center}
\begin{tikzpicture}[node distance=0.7cm]
\node [tcircle] (0) {$g_0^i$};
\node [right of=0] (0r) {.\ .\ .};
\node [tcircle,right of=0r] (0rr) {$g_0^n$};
\node [left of=0] (0l) {.\ .\ .};
\node [tcircle,left of=0l] (0ll) {$g_0^1$};
\node [draw,fit=(0rr) (0ll)] {};
\node [above of=0,node distance=2cm] (2) {.\ .\ .};
\node [left of=2, tcircle] (2l) {$g_j^1$};
\node [tcircle,right of=2] (2r) {$g_j^p$};
\node [draw, fit=(2l) (2r)] (2b) {};

\node [tcircle, left of=2l, node distance=3cm] (1r) {$g_1^q$};
\node [left of=1r] (1) {.\ .\ .};
\node [tcircle, left of=1] (1l) {$g_1^1$};
\node [draw, fit=(1l) (1r)] (1b) {};

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=3000,
  xmin=0, xmax=10,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=120,
  xmin=10, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\legend{\tactictoe proofs,original proofs}
\end{axis}
\end{tikzpicture}
\caption{Number of original and \tactictoe proofs with a number $x$ of tactic
units. For easier comparison of the distributions, the number of \tactictoe
proofs was
scaled by the inverse of \tactictoe's success rate $\frac{1}{0.662}$.}
\end{figure}

@@

The total effect on the readability of a proof script is depicted in
Example~\ref{ex:pretty}.
\todo{run without prettification}
\begin{example}\label{ex:pretty}\ \\
Extracted proof script:
\begin{lstlisting}[language=SMLSmall]
\end{lstlisting}
Minimized and prettified proof script:
\begin{lstlisting}[language=SMLSmall]
\end{lstlisting}
\end{example}

>>>>

\begin{definition}(search tree)\\
A search tree $\mathfrak{T}$ is a sixtuple
$(\mathbb{T},\mathbb{G},\mathbb{A},T,G,A)$
that respects the following conditions:
\begin{itemize}
\item $\mathbb{T}$ is a set of tactics, $\mathbb{G}$ is a set of goals
 and $\mathbb{A}$ is a set of nodes.
\item $T$ is a total function from $\mathbb{G}$ to $\mathcal{P}(\mathbb{T})$. It takes a
goal and return the set of tactics already applied to this goal.
\item $G$ is a total function from $\mathbb{A}$ to $\mathcal{P}(\mathbb{G})$. It takes a
node and returns the set of goals in this node.

\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. It takes a goal and a tactic and returns the node produced by the
application of the tactic to the goal. Its support $\mathit{Support}(A)$ is by 
definition $\lbrace (g,t) \in 
\mathbb{G} \times \mathbb{T}\ |\ t \in T(g)
\rbrace$.
\item If $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$. This is the 
main condition. The result of the application of a tactic $t$ 
to a goal $g$ is the list of goals contained in the node produced by $t$ from 
$g$.
\end{itemize}

@@

\begin{figure}{}
\begin{center}
\begin{tikzpicture}[node distance=0.7cm]
\node [tcircle] (0) {$g_0^i$};
\node [right of=0] (0r) {.\ .\ .};
\node [tcircle,right of=0r] (0rr) {$g_0^n$};
\node [left of=0] (0l) {.\ .\ .};
\node [tcircle,left of=0l] (0ll) {$g_0^1$};
\node [draw,fit=(0rr) (0ll)] (0b) {};
\node [left of=0ll] {$a_0$};
\node [above of=0,node distance=2cm] (2) {.\ .\ .};
\node [left of=2, tcircle] (2l) {$g_j^1$};
\node [tcircle,right of=2] (2r) {$g_j^p$};
\node [draw, fit=(2l) (2r)] (2b) {};
\node [left of=2l] {$a_j$};

\node [tcircle, left of=2l, node distance=3cm] (1r) {$g_1^q$};
\node [left of=1r] (1) {.\ .\ .};
\node [tcircle, left of=1] (1l) {$g_1^1$};
\node [draw, fit=(1l) (1r)] (1b) {};
\node [left of=1l] {$a_1$};

@@

\begin{figure}[h]
\centering
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=3000,
  xmin=0, xmax=10,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=1]
\begin{axis}[
  legend style={anchor=north east, at={(0.9,0.9)}},
  width=0.5*\textwidth,
  height=0.5*\textwidth,
  ymin=0, ymax=120,
  xmin=10, xmax=50,
  xtick={},
  ytick={},
  cycle list name=my black]
\addplot table[x=length, y=proofs] {data/tactictoe_proof_length};
\addplot table[x=length, y=proofs] {data/original_proof_length};
\legend{\tactictoe proofs,original proofs}
\end{axis}
\end{tikzpicture}
\caption{Number of original human proofs and (minimized see Section) \tactictoe 
proofs with 
a number $x$ of tactic
units. For easier comparison of the distributions, the number of \tactictoe
proofs was
scaled by the inverse of \tactictoe's success rate $\frac{1}{0.662}$.}
\end{figure}

@@

The total effect on the readability of a proof script is depicted in
Example~\ref{ex:pretty}.
\todo{run without prettification}
\begin{example}\label{ex:pretty}\ \\
Discovered proof script for the theorem \texttt{EVERY\_MAP}
\begin{lstlisting}[language=SMLSmall]
boolLib.REWRITE_TAC [DB.fetch "list" "EVERY_CONJ", DB.fetch "list" "EVERY_MEM", 
  DB.fetch "list" "EVERY_EL", ldots ,  combinTheory.o_DEF] THEN 
BasicProvers.Induct_on [HolKernel.QUOTE " (*#loc 1 11380*)l"] THENL
  [BasicProvers.SRW_TAC [] [],
   simpLib.ASM_SIMP_TAC (BasicProvers.srw_ss ()) [boolLib.DISJ_IMP_THM, 
     DB.fetch "list" "MAP", DB.fetch "list" "CONS_11", boolLib.FORALL_AND_THM]]

\end{lstlisting}
Minimized and prettified proof script:
\begin{lstlisting}[language=SMLSmall]
Induct_on `l` THENL 
  [SRW_TAC [] [], ASM_SIMP_TAC (srw_ss ()) [DISJ_IMP_THM, FORALL_AND_THM]]
\end{lstlisting}
\end{example}
